Cats and Dogs Recognition

### 2013-12-06 paper.tex

>>>>

\begin{thebibliography}{99}
\bibitem{viola} 
\bibitem{sun}
\bibitem{golle} 
\bibitem{asirra} J. Elson, J. Douceur, J. Howell and J. Saul. \textit{Asirra: a CAPTCHA that exploits interest-aligned manual image categorization.} In Proc. of ACM CCS 2007, pp. 366-374.
\end{thebibliography}
\end{document}
=======
\documentclass[12pt]{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{stmaryrd}
\usepackage{graphicx}
\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{8.5in}
\hyphenpenalty = 10000
\pagenumbering{gobble}
\title{Cats and Dogs Recognition}
\author{Chongyuan Xiang, Min Zhang, and Weixin Chen}
\begin{document}
\maketitle
\begin{abstract}
In this paper, we focus on the problem of classifying images of cats and dogs, which is also known as one Asirra. We use three schemes to tackle the problem. First, we use information of the whole image; second, we use information of the animal body; third, we only use features from the head. The asymptotic behavior of the classification improves when we restrict the regions to the more distinguishable ones. We obtain 82.3$\%$, 84.4$\%$, and 85.6$\%$ under our best choice of features and voting scheme.  We anticipate that the accuracy of the second and third scheme will improve moderately if including more training samples.    
\end{abstract}

\section {Combination of Color and Texture Feature}
Assume that color feature vector has a length of $N_c$, the texture feature has a length of $N_t$. Our first approach is to concatenate the two feature vectors into a longer feature vector with a length of $N_c + N_t$. Then we will run boosting algorithm using the new feature vector. \\
The second approach is combining two classifiers instead of combing two feature vectors. Recall that for boosting classifier, each picture will have a voting. Assume that classfier 1 gives the picture a voting $v_1$, and classifier 2 gives the picture a voting $v_2$. Given parameter $\alpha$, we calculate a new voting $ v = \alpha \times v_1 + (1-\alpha) \times v_2$. We use different $\alpha$ to form different classifiers and use them to test on our training examples, and find one with the highest correction rate.
\begin{table}[h]
\caption{Combined Feature Training Result}
\centering
\begin{tabular}{| p{8cm}| l | l | l | l |}
\hline
Two feature vectors $F_1$ and $F_2$ & \multicolumn{4}{|c|}{Correction Rate} \\ \cline{2-5}
 & $F_1$ & $F_2$ & approach1 & approach2 \\
\hline
$F_1$ = RGB($n=1,x=10,y=10,z=10$), $F_2$ = TF1($n=16,N_f=24$) & 71.9\% & 66.5\% & 73.1\% & 73.8 \% \\
\hline
$F_1$ = HSV($n=3,x=10,y=10,z=10$), $F_2$ = TF1($n=8,N_f=24$) & 72.7\% & 67.1\% & 73.6\% & 74.5 \% \\
\hline
\end{tabular}
\end{table}\\
From Table 3, we can see that both of the approaches achieve a better correction rate, and approach 2 is better than approach 1.

Analysis of result. Not satisfying possibly because not aligned and normalized.
\subsection{Cascade of Classifier}
The idea is similar to a decision tree. At each layer of the cascade is a classifier and an example will be rejected immediately if it is rejected by one layer. When training the classifier, at each layer, we use boosting algorithms to select important features and find a reasonable threshold that almost all positive training examples will be left and a decent amount of negative training examples will be rejected. This way, negative examples will be rejected quickly while only a small number of positive examples will be misclassified. For the same reason, a large amount of negative examples are required. In $\cite{viola}$, Viola and Jones trained 9544 face images and 350 million background images to get a 37 layers of cascade classifier. In our project, we trained 400 cat heads, 400 dog heads, and 20 thousand background images with a 15 layers of cascade. We arrived at 4$\%$ false negative rate and $1\%$ false positive rate.

some result compare adaboost and logtiboost compare different layers result
